A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-29 manuscript.Rmd

Describing the preregistration in form of a journal article requires authors to follow the same standards that also ensure that research articles are comprehensive enough to replicate the described study.
<!-- I dont understand this sentence -->
One particular advantage is the foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless, it can be fruitful to consult preregistration templates because of their strong focus on formulating a comprehensive methods section.

@@

To write a PAC, researchers should start by drafting a manuscript in the form of an R Markdown.
When they have completed the method section, they should begin writing code.
We suggest writing three functions for each hypothesis tested, one for the planned analysis, one for simulating the data and one for reporting the results.
At the heart of a PAC lies the planned analysis, so researchers should first draft a function called `planned_analysis()` that fits the description in their method section.
This function should receive the data and derive relevant results from it.

@@

As usual, researchers state why they are interested in their research question in the section "Introduction" and provide the necessary background information and literature to understand the context and purpose of the research question.
This example is drastically shortened for purposes of illustration:

@@

We implemented a mechanism that only uses simulated data when the actual data is not yet available for the results section.
This mechanism also warns readers if these results are based on simulated data. <!--AB how does it warn?-->
As soon as the actual data are available, the simulated data is no longer used, and the results represent the actual empirical results of the study. <!--AB how exactly does the script know?-->

>>>>

Describing the preregistration in form of a journal article requires authors to follow the same standards that also ensure that research articles are comprehensive enough to replicate the described study.
One particular advantage is the foundation in existing literature where the introduction and theoretical background provide the basis for the studies' design.
Nevertheless, it can be fruitful to consult preregistration templates because of their strong focus on formulating a comprehensive methods section.

@@

To write a PAC, researchers should start by drafting a manuscript in the form of an R Markdown.
When they have completed the method section, they should begin writing code.
We suggest writing three functions for each planned hypothesis, one for the planned analysis, one for simulating the data and one for reporting the results.
At the heart of a PAC lies the planned analysis, so researchers should first draft a function called `planned_analysis()` that fits the description in their method section.
This function should receive the data and derive relevant results from it.

@@

As usual, researchers state why they are interested in their research question in the section "Introduction" and provide the necessary background information and literature to understand the context and purpose of the research question.
This example is drastically shortened for illustration purposes:

@@

We implemented a mechanism that only uses simulated data when the actual data is not yet available  (in this example if the file `data/data.csv` does not exist)for the results section.
This mechanism also warns readers if these results are based on simulated data.
The warning is colored red to avoid any confusion between mock and actual results.
As soon as the actual data are available, the simulated data is no longer used, and the results represent the actual empirical results of the study.
